---
title: "A5"
author: "Abhishek Ravi Chandran, Chinmayee Vaidya"
date: "March 14, 2016"
output: pdf_document
---

# Design
In this assignment we try to find the number of connecting flights for each carrier for every year.

In the mapper class we use a custom key where we write every record twice differentiating them by a flag(type). 0 for incoming flights and 1 for outgoing flights.

The logic for handling overnight flights is already present in the method where we set values to our object after parsing it.

We sort the data to make sure that all incoming flights are sent to the reducer first, followed by all the outgoing flights.
This is achieved by having a custom key, custom sort comparator and a custom group comparator. By using the group comparator we ensure that each carrier and year are chosen as the natural key to send all records grouped with this key to a single reducer.

In the reducer, we put all the incoming flights into a map with the key as city(destination), so all flights incoming to city 'a' will be under the key 'a'. The records are stored in a TreeSet which will sort all the flights stored according to their scheduled arrival time.

When we start getting outgoing flights, for each record we fetch all flights incoming to the same city as the origin city of this record, by getting the records from the map. Since the values are sorted, we keep checking for connections until we reach a record where the time difference is more than 360 minutes, meaning any flight after this will not form a connection as it is outside the time window. This ensures that not all flights are not compared reducing the number of comparisons.

Conditions for a connection:
A Connections is made when 
A.destination = B.Origin && [(B.scheduledDeparture - A.ScheduledArrival) >=30 mins && <=6hrs]

A connection is said to be bad if
flight A is cancelled or( B.actualDeparture - A.actualArrival) < 30 mins

Performance:
The program runs for ~22 minutes in a 5 m3.xlarge cluster configuration for 2 years data.

```{r, echo=FALSE,fig.width=15, fig.height=7,warning=FALSE,message=FALSE}

files <- dir("output",pattern = 'pa\\.*')
path=paste(getwd(),"output", sep="/")
results <- data.frame() 

for(f in files){
  r <- read.csv(paste(path,f,sep="/"), header = FALSE)
  results <- rbind(results,r)
}
names(results) <- c("Carrier", "Year", "Connection","Missed Connection")
sr <- results[order(results$Carrier,results$Year),]
```


#Output:
```{r echo=FALSE}
print(sr,row.names=FALSE)
```

#Assumptions:

We have not taken care of Year rollover as the year is part of the key. We assume that the number of flights will be minimal for the end of the year and should not change the result much.
